Models

### 2022-04-27 analysis/05_model_metrics.Rmd

      df <- tidy(fit$result) %>% 
        bind_rows(group_slopes, slope_constrasts) %>%
        mutate(metric = metric_name, model = list(fit$result), model_id = model_id,
               n_ts = n_distinct(fit_data$rarefyID),
               warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
    }else{
      return(tibble())
    }
  }else{

@@

    tidy(fit$result) %>%
      mutate(metric = metric_name, model = list(fit$result), model_id = model_id, 
             n_ts = n_distinct(fit_data$rarefyID),
             warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
  }
}

@@

Write out table of model estimates for manuscript
```{r}
metric_model_table %>% 
  filter(model_id == "base", metric %in% c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")) %>% 
  select(-c(model_id, warning, statistic, df)) %>% 
  write_csv(here::here("figures", "man_model_table.csv"))
```

>>>>

      df <- tidy(fit$result) %>% 
        bind_rows(group_slopes, slope_constrasts) %>%
        mutate(metric = metric_name, model = list(fit$result), model_id = model_id,
               n_ts = n_distinct(fit_data$rarefyID),
               formula = formula,
               warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
    }else{
      return(tibble())
    }
  }else{

@@

    tidy(fit$result) %>%
      mutate(metric = metric_name, model = list(fit$result), model_id = model_id, 
             n_ts = n_distinct(fit_data$rarefyID),
             formula = formula,
             warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
  }
}

@@

Write out table of model estimates for manuscript
```{r}
#manuscript table
metric_model_table %>% 
  filter(model_id == "base", metric %in% c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")) %>% 
  select(-c(model_id, warning, statistic, df)) %>% 
  write_csv(here::here("figures", "man_model_table.csv"))

#supplement of complete model output
metric_model_table %>%
  select(-c(model_id, n_ts, warning, lower.CL, upper.CL, significant)) %>%
  write_csv(here::here("paper", "model_estimates_supp.csv"))

```
